\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage[export]{adjustbox}
\usepackage{multicol}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage{color}
\usepackage{lipsum}
\usepackage[scale=0.90]{geometry}

\setlength{\hintscolumnwidth}{4cm}

\firstname{Simon}
\familyname{Legg}

\title{Curriculum Vitae}

% This command effectively comments out anything within it
\newcommand{\comment}[1]{} 

%----------------------------------------------------------------------------------------

\begin{document}

\textit{\Huge{\textcolor{black}{Simon Legg}}}

\hrulefill

%--------------------------------------
%	CONTACT
%--------------------------------------

\section{Contact}

\cvitem{LinkedIn}{https://www.linkedin.com/in/simon-legg}
\cvitem{Email}{leggsimon@gmail.com}
\cvitem{GitHub}{https://github.com/leggsimon}

%---------------------------------------
%	WORK EXPERIENCE
%---------------------------------------

\section{Work Experience}

\cvitem{Jul. 2022 -- May 2023}{\textbf{Shopify} \textit{Remote} -- Senior Software Engineer}
\renewcommand{\listitemsymbol}{\textcolor{black}{-~}}
\cvlistitem{Increased parsed orders surfaced in the Shop App by 1.5x writing performant, bespoke parsers for email templates at scale.}
\cvlistitem{Leveraged LLMs to create an automated email parsing system hit 40m times per day.}

\cvitem{Apr. 2021 -- May 2022}{\textbf{Yara International} \textit{Berlin, Germany} -- Senior Software Engineer}
\renewcommand{\listitemsymbol}{\textcolor{black}{-~}}
\cvlistitem{Managed responses to customer facing incidents, reducing visible impact to customers as quickly as possible, and coordinating responses from engineers and communicating with Customer Service team and Product stakeholders on updates.}
\cvlistitem{Advocated for, and introduced tickets on our roadmap for improved Observability and Monitoring of frontend architecture and product stability, to speed up diagnosis of complex bugs and improve our response time to live incidents.}

\cvitem{Oct. 2019 -- Mar. 2020}{\textbf{Get Your Guide} \textit{Berlin, Germany} -- Senior Software Engineer}
\renewcommand{\listitemsymbol}{\textcolor{black}{-~}}
\cvlistitem{Worked on Get Your Guide’s user facing website aimed at the post purchase user journey. Helped to encourage a culture of front-end development with an accessible and performant web in mind. }

\cvitem{Apr. 2018 -- Aug. 2019}{\textbf{Financial Times} \textit{London, United Kingdom} -- Senior Software Engineer}
\cvitem{Aug. 2016 -- Apr. 2018}{\textbf{Financial Times} \textit{London, United Kingdom} -- Software Engineer}
\cvitem{Oct. 2015 -- Aug. 2016}{\textbf{Financial Times} \textit{London, United Kingdom} -- Junior Software Engineer}
\renewcommand{\listitemsymbol}{\textcolor{black}{-~}}
\cvlistitem{Helped rebuild FT.com, which launched late 2016 becoming one of the fastest newspaper websites in the industry.}
\cvlistitem{Was the technical lead in a cross-functional team heading up two B2B products responsible for £40m annual revenue to the Financial Times. This has involved a lot of code review, handling and delivering stakeholders' vision of the products, and steering the technical architecture of the products.}



%---------------------------------------
%	EDUCATION
%---------------------------------------

\section{Education}

\cvitem{Jun. 2015 -- Aug. 2015}{\textbf{Makers Academy} \textit{London, United Kingdom} \newline { Web Development Bootcamp }}

%------------------------------------
%	SKILLS
%------------------------------------

\section{Skills}

\cvitem{\textbf{Experienced}}{JavaScript, TypeScript, HTML5, CSS3, React, Node.js, Git}
\cvitem{\textbf{Intermediate}}{Ruby on Rails, Python, Bash}

\end{document}
